Explorations to Optimize the Parareal Algorithm \\to Solve ODEs in Given Applications

### 2014-12-10 paper.tex
wrote some stuff

% Possible packages - uncomment to use
\usepackage{amsmath} % Needed for math stuff
%\usepackage{lastpage}sss% Finds last page
\usepackage{amssymb} % Needed for some math symbols
\usepackage{graphicx}% Needed for graphics
\usepackage[usenames,dvipsnames]{xcolor} % Needed for graphics and color
%\usepackage{setspace}sss% Needed to set single/double spacing
\usepackage{float} % Better placement of figures & tables
\usepackage{hyperref} % Can have actual links
\usepackage{mathpazo}
\usepackage[linesnumbered,vlined,ruled]{algorithm2e} % algorithm
\usepackage{microtype}

@@

% Sets the page margins to 1 inch each side
\usepackage[margin=1in]{geometry}
% force pictures to go where you want
\usepackage{float}

\geometry{letterpaper}
%\addtolength{\oddsidemargin}{-0.875in} 
%\addtolength{\evensidemargin}{-0.875in} 
%\addtolength{\textwidth}{1.75in} 
%\addtolength{\topmargin}{-.875in} 
%\addtolength{\textheight}{1.75in}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=0.75\linewidth]{parareal_visualization.png}
\caption{Graphical representation of the parareal scheme.}
\label{fig:pararealvis}
\end{center}
\end{figure}

@@

\[
y'(t) = f(t, y) = \lambda y, \, \, y(0) = 1
\]
\[
y''(t) + 2y'(t) + 5y(t) = 0, \, \, y(0) = 1, \, y'(0) = 0.
\]

We ran the algorithm on different numbers of processors and varied $k$ and $Q$.

%Varying Iterations:

Varying Quality Factor:
We define the quality factor in this case for how many times smaller the Euler
method used for $g_{\textnormal{fine}}$ is compared to the Euler method used for
$g_{\Delta t}$.

\begin{figure}
\begin{center}
\includegraphics[width=0.75\textwidth]{data/runtime_vs_cpus.pdf}
\caption{Running time vs. number of CPUs.}
\label{fig:run_v_cpu}
\end{center}
\end{figure}

Figure~\ref{fig:run_v_cpu} shows the running time (wall clock) for the Parareal
algorithm

\begin{figure}
\begin{center}
\includegraphics[width=0.75\linewidth]{data/error_vs_corrections.pdf}
\caption{Error vs. number of correction steps.}
\label{fig:err_v_k}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.75\linewidth]{data/error_vs_qualityfactor.pdf}
\caption{Error vs. quality factor of the fine operator}
\label{fig:err_v_q}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.75\linewidth]{data/runtime_vs_corrections.pdf}
\caption{Running time as a function of the number of correction steps.}
\label{fig:run_v_k}
\end{center}
\end{figure}

>>>>

% Possible packages - uncomment to use
\usepackage{amsmath} % Needed for math stuff
%\usepackage{lastpage} % Finds last page
\usepackage{amssymb}  % Needed for some math symbols
\usepackage{graphicx} % Needed for graphics
\usepackage[usenames,dvipsnames]{xcolor} % Needed for graphics and color
%\usepackage{setspace} % Needed to set single/double spacing
\usepackage{float} % Better placement of figures & tables
\usepackage{hyperref} % Can have actual links
\usepackage{mathpazo}
\usepackage[linesnumbered,vlined,ruled]{algorithm2e} % algorithm
\usepackage{microtype}

@@

% Sets the page margins to 1 inch each side
\usepackage[margin=1in]{geometry}
\geometry{letterpaper}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.75\linewidth]{parareal_visualization.png}
\caption{Graphical representation of the parareal scheme.}
\label{fig:pararealvis}
\end{center}
\end{figure}

@@

Example 1:
\[
y'(t) = f(t, y) = \lambda y, \, \, y(0) = 1
\]

Example 2:
\[
y''(t) + 2y'(t) + 5y(t) = 0, \, \, y(0) = 1, \, y'(0) = 0.
\]

We ran the algorithm on different numbers of processors and varied $k$ and $Q$.
We define the quality factor $Q$ in this case for how many times smaller the
Euler method used for $g_{\textnormal{fine}}$ is compared to the Euler method
used for $g_{\Delta t}$.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.75\textwidth]{data/runtime_vs_cpus.pdf}
\caption{Running time vs. number of CPUs.}
\label{fig:run_v_cpu}
\end{center}
\end{figure}

Figure~\ref{fig:run_v_cpu} shows the running time (wall clock) for the Parareal
algorithm compared to different number of CPUs used. The serial version is the
Euler method with $Q$ times as many steps. As we can see, the running time
decreases as more processors are added. However, there is a base time associated
with setting up the parallel infrastructure, so asymptotically the running time
is nonzero.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.75\linewidth]{data/error_vs_corrections.pdf}
\caption{Error vs. number of correction steps.}
\label{fig:err_v_k}
\end{center}
\end{figure}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.75\linewidth]{data/error_vs_qualityfactor.pdf}
\caption{Error vs. quality factor of the fine operator}
\label{fig:err_v_q}
\end{center}
\end{figure}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.75\linewidth]{data/runtime_vs_corrections.pdf}
\caption{Running time as a function of the number of correction steps.}
\label{fig:run_v_k}
\end{center}
\end{figure}
